\section{Numerical solution techniques}\label{sec:numerical_techniques}
The discussion to this point has outlined the formulation of the \methodAcronym\ method. We now consider numerical solution techniques. 
\KTC{Passive voice:} As \methodAcronym\ displays commonalities with optimal
control problems, a large existing body of work can be leveraged. This section
discuses a variety of such techniques and outlines how they can be used to
solve the \methodAcronym\ system. We focus primarily on \KTC{earlier we kept
saying 
direct (i.e.,
	discretize-then-optimize) and indirect (i.e., optimize-then-discretize).
	Let's be consistent when we re-introduce it here.}
optimize direct and indirect methods for \spatialAcronym\ trial subspaces, 
and then briefly outline direct and indirect methods for \spaceTimeAcronym\ trial subspaces. 
%Equation~\ref{eq:obj_gen_slab} displays commonalities with optimal control problems. For timeslabs $n = 1,\ldots,\nslabs$, the objective is to find the \textit{function} $\genstate^n(t)$ that minimizes the \textit{functional} $ \mathcal{J}^n$. The distinction between Eq.~\ref{eq:obj_gen_slab} and traditional optimal control problems is that, in the form presented in Eq.~\ref{eq:obj_gen_slab}, (1) there is not a controller and (2) there is no system that describes the dynamics for the generalized coordinates. 
%Techniques used to solve optimal control problems can be leveraged to solve Eq.~\ref{eq:obj_gen_slab} (or, equivalently, Eqs.~\eqref{eq:tclspg_oc1} and~\eqref{eq:tclspg_oc2}).

\subsection{\spatialAcronym: direct and indirect methods}
Numerical techniques to
solve optimal control problems can be classified as either
\textit{direct} or \textit{indirect}
methods~\cite{conway_optimalcontrolreview}.  Direct \KTC{Typo:} method eschew
the calculus of variations \KTC{weird to say they `eschew' calculus. Find
something better here}
and attempt to ``directly" solve the optimization problem~\eqref{eq:tclsrm} by first
numerically discretizing the system and objective functional and ``transcribing"
the infinite dimensional problem into a finite-dimensional nonlinear
programming (optimization) problem. Direct approaches thus ``discretize then optimize."
Indirect methods, on the other hand, leverage the calculus of variations to
derive the Euler--Lagrange equations, which comprise the first-order
optimality conditions\KTC{use endash}~\eqref{eq:lspg_continuous}-\eqref{eq:lspg_bcs} associated with the objective 
functional. Indirect methods then solve (numerically) the Euler--Lagrange equations. Thus, indirect methods ``optimize then discretize," and 
solve the optimization problem
``indirectly". \KTC{Passive voice:} For both direct and indirect methods, a variety of
discretization/solution approaches are then possible. Collocation methods,
finite elements, spectral methods, shooting methods, etc., are all examples of
plausible solution techniques.  

In the present context, both direct and indirect methods \KTC{Passive voice:}
are investigated to solve \methodAcronym\ with \spatialAcronym\ trial
subspaces. We consider: \KTC{Weird capitalization and bulleting. Make
consistent with earlier in the paper, e.g., introduction, and don't break into
sub-bullet, looks ugly.}

\begin{itemize} \item Discretize then Optimize (Direct Methods): 
\begin{itemize}
\item Discretize and then optimize approaches are outlined for linear multistep methods. 
\end{itemize} 
\item Optimize then Discretize (Indirect Methods): 
\begin{itemize} 
\item An indirect method leveraging the forward-backward sweep algorithm is outlined 
to solve~\eqref{eq:lspg_continuous}-\eqref{eq:lspg_bcs}. 
 \end{itemize} 
\end{itemize} 
\KTC{Passive voice:} It
is emphasized that a variety of other approaches exist. A detailed exploration
of additional approaches is the subject of future work.
Section~\ref{sec:direct}  outlines direct solution approaches based on linear
multistep methods, while Section~\ref{sec:indirect} outlines the indirect
solution approach. 



\input{section4/spatial_numerical}
\input{section4/spacetime_numerical}
